Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
Fixed some more spacing issues

\PassOptionsToPackage{usenames,dvipsnames,svgnames,table}{xcolor}
\documentclass[acmsmall,screen,anonymous]{acmart}
\settopmatter{printacmref=false}

@@

    $\PutL{} \App \StringAlt \App \String$
    & =
    & $\begin{cases*}
        \Lens_1.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$\\
        \Lens_2.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_1.\CreateLOf{\StringAlt} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_2.\CreateLOf{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.

\[
  \centering
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
  {
    \IterateLensOf{\Lens} \OfType
    \StarOf{\BRegex}
    \Leftrightarrow
    \StarOf{\BRegexAlt}
  }
\]
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\ldots\String_n$
%    & =
%    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\
%    
%    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
%    & =
%    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\
%    
%    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
%    & =
%    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
%        \Lens.\CreateROf{\String_i} & otherwise
%      \end{cases*}$\\
%    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
%    & =
%    & $\String_1'\ldots\String_n'$ where $\String_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
%        \Lens.\CreateROf{\StringAlt_i} & otherwise
%      \end{cases*}$
%  \end{tabular}
%\end{center}
The \IterateLens lens deals with iterated data.

\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

@@

\[
  \centering
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
  {
    \InvertOf{\Lens} \OfType \BRegexAlt \Leftrightarrow \BRegex
  }
\]
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \StringAlt$ & = & $\Lens.\CreateLOf{\StringAlt}$\\
%    $\CreateL{} \App \String$ & = & $\Lens.\CreateROf{\String}$\\
%    $\PutR{} \App \StringAlt \App \String$ & = & $\Lens.\PutLOf{\StringAlt}{\String}$\\
%    $\PutL{} \App \String \App \StringAlt$ & = & $\Lens.\PutROf{\String}{\StringAlt}$
%  \end{tabular}
%\end{center}
Inverting reverses the direction of a lens: creating on the right becomes creating on the left and vice versa, and putting on the right becomes putting on the left and vice versa. The invert combonator is particularly useful when chaining many compositions together, as it can be used to align the central types.

\[
  \centering
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt\\
    \BRegex \SSREquiv \BRegex'\\
    \BRegexAlt \SSREquiv \BRegexAlt'
  }
  {
    \Lens \OfType \BRegex' \Leftrightarrow \BRegexAlt'
  }
\]
Type equivalence enables a lens of type $S \Leftrightarrow T$ to be used as a
lens of type $S' \Leftrightarrow T'$ if $S$ equivalent to $S'$ and $T$ is
equivalent to $T'$. Type equivalence is useful both for addressing type
annotations, and for making well-typed compositions.

@@

The procedure \PCF{\Continue} returns false based on the how long the search has
been going, and how hard it expects the next class of problems to be. In
particular, if $\PCF{PQ.Peek}(pq) = (\Regex,\RegexAlt)$, that RE pair is at
distance $d$, the number of pairs in $pq$ at distance $d$ is $n$, and the
current best lens has cost $c$:
\begin{gather*}
  \Call{Continue}{pq} := c >= d + \Log_2(n)
\end{gather*}

@@

For these types of situations, users can input a custom number, $t$, to
customize the strictness of the termination condition. In particular, if
$\PCF{PQ.Peek}(pq) = (\Regex,\RegexAlt)$, that RE pair is at distance $d$, the
number of pairs in $pq$ at distance $d$ is $n$, and the current best lens has
cost $c$:
\begin{gather*}
  \Call{Continue}{pq} := c >= \Min(d + \Log_2(n) - t, 0)
\end{gather*}
With a positive $t$, the termination condition is more strict, and the algorithm
will spend longer searching for more likely lenses. With a negative $t$ the
termination condition is less strict, and the algorithm will spend less time
searching for more likely lenses.  Our default $t$ is set to $0$.

>>>>

\PassOptionsToPackage{usenames,dvipsnames,svgnames,table}{xcolor}
\documentclass[acmsmall,review,screen,anonymous]{acmart}
\settopmatter{printacmref=false,printccs=false}

@@

    $\PutL{} \App \StringAlt \App \String$
    & =
    & $\begin{cases*}
        \Lens_1.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$\\
        \Lens_2.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_1.\CreateLOf{\StringAlt} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_2.\CreateLOf{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\ldots\String_n$
%    & =
%    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\
%    
%    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
%    & =
%    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\
%    
%    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
%    & =
%    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
%        \Lens.\CreateROf{\String_i} & otherwise
%      \end{cases*}$\\
%    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
%    & =
%    & $\String_1'\ldots\String_n'$ where $\String_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
%        \Lens.\CreateROf{\StringAlt_i} & otherwise
%      \end{cases*}$
%  \end{tabular}
%\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

@@

\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
\inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
  {
    \IterateLensOf{\Lens} \OfType
    \StarOf{\BRegex}
    \Leftrightarrow
    \StarOf{\BRegexAlt}
  }
  $
  &
  $
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
  {
    \InvertOf{\Lens} \OfType \BRegexAlt \Leftrightarrow \BRegex
  }
  $
\end{tabular}
\end{centermath}
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \StringAlt$ & = & $\Lens.\CreateLOf{\StringAlt}$\\
%    $\CreateL{} \App \String$ & = & $\Lens.\CreateROf{\String}$\\
%    $\PutR{} \App \StringAlt \App \String$ & = & $\Lens.\PutLOf{\StringAlt}{\String}$\\
%    $\PutL{} \App \String \App \StringAlt$ & = & $\Lens.\PutROf{\String}{\StringAlt}$
%  \end{tabular}
%\end{center}
The \IterateLens lens deals with iterated data, while inverting reverses the direction of a lens: creating on the right becomes creating on the left and vice versa, and putting on the right becomes putting on the left and vice versa. The invert combonator is particularly useful when chaining many compositions together, as it can be used to align the central types.
\[
  \centering
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt\\
    \BRegex \SSREquiv \BRegex'\\
    \BRegexAlt \SSREquiv \BRegexAlt'
  }
  {
    \Lens \OfType \BRegex' \Leftrightarrow \BRegexAlt'
  }
\]

Type equivalence enables a lens of type $S \Leftrightarrow T$ to be used as a
lens of type $S' \Leftrightarrow T'$ if $S$ equivalent to $S'$ and $T$ is
equivalent to $T'$. Type equivalence is useful both for addressing type
annotations, and for making well-typed compositions.

@@

The procedure \PCF{\Continue} returns false based on the how long the search has
been going, and how hard it expects the next class of problems to be. In
particular, if $\PCF{PQ.Peek}(pq) = (\Regex,\RegexAlt)$, that RE pair is at
distance $d$, the number of pairs in $pq$ at distance $d$ is $n$, and the
current best lens has cost $c$:
\begin{gather*}
  \Call{Continue}{pq} := c > d + \Log_2(n)
\end{gather*}

@@

For these types of situations, users can input a custom number, $t$, to
customize the strictness of the termination condition. In particular, if
$\PCF{PQ.Peek}(pq) = (\Regex,\RegexAlt)$, that RE pair is at distance $d$, the
number of pairs in $pq$ at distance $d$ is $n$, and the current best lens has
cost $c$:
\begin{gather*}
  \Call{Continue}{pq} := c > \Min(d + \Log_2(n) - t, 0)
\end{gather*}
With a positive $t$, the termination condition is more strict, and the algorithm
will spend longer searching for more likely lenses. With a negative $t$ the
termination condition is less strict, and the algorithm will spend less time
searching for more likely lenses.  Our default $t$ is set to $0$.
